Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
LUCAS I edited your section, feel free to change things back

\subsection{List functions}
Our list function domain consists of hand-designed concepts from which we
sample tasks, so there is no ``ground truth'' formal DSL from which these
tasks are generated. Additionally, few of these tasks are concatenative ---
many of them represent distinct operations.
Tasks in this domain are solved by functions that take as input an integer
or a list of integers, and have as output either a Boolean, an integer, a
list of Booleans, or a list of integers.  There are 225 tasks in total, some
of which are shown in Tbl.~\ref{listexamples}.

We take approaches from two different initial DSLs, \emph{base} and
\emph{rich}, and assess their performance. The base DSL starts with only
low-level primitives such as \code{mapi}, \code{reducei}, and
\code{if}, whereas the rich DSL includes some common structure that can be
built from these such as \code{all}, \code{filter}, \code{slice}, and
\code{index}.
Both are capable of solving all tasks supplied by our dataset.
See Supplement for details on these DSLs.

We found that this domain was difficult to tackle without starting from a
relatively rich DSL, and even then it was still hard to solve all tasks. Our
algorithm, like human learners, requires a spectrum of problems ranging from
easy to hard. Without this curriculum, \system cannot get off the ground.
The behavior with the base DSL illustrates this, because the initial set of
primitives is not paired with a sufficiently large and graded curriculum.

\begin{table}
\centering
\begin{tabular}{lll}
  \toprule
  Name & Input & Output \\\midrule
  add-3 & [1\, 2\, 3\, 4] & [4\, 5\, 6\, 7] \\
  append-4 & [7\, 0\, 2] & [7\, 0\, 2\, 4] \\
  len & [3\, 5\, 12\, 1] & 4 \\
  range & 3 & [1\, 2\, 3] \\
  has-2 & [4\, 5\, 7\, 4] & \code{false} \\
  has-head-in-tail & [4\, 5\, 7\, 4] & \code{true} \\
  repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
  drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
  \bottomrule
\end{tabular}
\caption{Simple tasks from our list function domain. We used 15 input/output
  examples for each task to reduce ambiguity in the task's function,
  ensuring solutions achieve the desired concept.}
\label{listexamples}
\end{table}

>>>>

\subsection{List functions}
Synthesizing programs that manipulate data structures is
a widely studied problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of
learning functions that manipulate lists.
We created 225 Lisp-style list manipulation tasks,
each with 15 input/output examples (Tbl.~\ref{listexamples}).
Our data set is challenging along two dimensions:
many of the functions are very complicated,
and the agent must learn to solve these complicated problems from only 225 tasks.

%% Our list function domain consists of hand-designed concepts from which we
%% sample tasks, so there is no ``ground truth'' formal DSL from which these
%% tasks are generated. Additionally, few of these tasks are concatenative ---
%% many of them represent distinct operations.
%% Tasks in this domain are solved by functions that take as input an integer
%% or a list of integers, and have as output either a Boolean, an integer, a
%% list of Booleans, or a list of integers.  There are 225 tasks in total, some
%% of which are shown in Tbl.~\ref{listexamples}.

We evaluate \system starting from two different initial DSLs, \emph{base} and
\emph{rich}. The base DSL starts with only
low-level primitives such as \code{mapi}, \code{reducei}, and
\code{if}, whereas the rich DSL includes some common structure that can be
built from these such as \code{all}, \code{filter}, \code{slice}, and
\code{index}.
Both are capable of solving all tasks supplied by our dataset.
See Supplement for details on these DSLs.

We found  this domain  difficult to tackle without starting from 
the rich DSL. Our
algorithm, like human learners, requires a spectrum of problems ranging from
easy to hard. Without this curriculum, we cannot get off the ground.
%The behavior with the base DSL illustrates this phenomena  because the initial set of
%primitives is not paired with a sufficiently large and graded curriculum.

\begin{table}
\centering
\begin{tabular}{lll}
  \toprule
  Name & Input & Output \\\midrule
  add-3 & [1\, 2\, 3\, 4] & [4\, 5\, 6\, 7] \\
  append-4 & [7\, 0\, 2] & [7\, 0\, 2\, 4] \\
  len & [3\, 5\, 12\, 1] & 4 \\
  range & 3 & [1\, 2\, 3] \\
  has-2 & [4\, 5\, 7\, 4] & \code{false} \\
  has-head-in-tail & [4\, 5\, 7\, 4] & \code{true} \\
  repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
  drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
  \bottomrule
\end{tabular}
\caption{Sample tasks from our list function domain. %% We used 15 input/output
  %% examples for each task to reduce ambiguity in the task's function,
  %% ensuring solutions achieve the desired concept.
}
\label{listexamples}
\end{table}
